\documentclass[../Report.tex]{subfiles}

\begin{document}

\begin{center}
    \textbf{ACKNOWLEDGEMENT}
\end{center}
The satisfaction that accompanies the successful completion of any task would be incomplete without the mention of the people who made it 
possible and whose encouragement and guidance has been a source of inspiration throughout the course of the project.\par

It is a great pleasure to convey our profound sense of gratitude to our Principal \textbf{Dr. Nayanathara K. S} and 
\textbf{\hodName, Head of the CSE Department}, CVR College of Engineering for being kind enough for arranging the necessary facilities 
for executing the project in the college.\par

We would like to express our sincere gratitude to our guide, \textbf{\guideName, Associate Prof., CSE Dept.,} CVR College of Engineering,
whose guidance and valuable suggestions have been indispensable to bring
about the successful completion of our project.\par

We wish to acknowledge special thanks to the Project Coordinator \textbf{Dr.M.Jaiganesh, CSE Dept.,} for assessing seminars, 
inspiration, moral support and giving us valuable suggestions in our project.\par

We would also like to express our gratitude to all the staff members and lab faculty, department of 
\textbf{Computer Science and Engineering,} \textbf{\collegeName} for the constant help and support.\par

We wish a deep sense of gratitude and heartfelt thanks to management for providing excellent lab facilities and tools. Finally, 
we thank all those whose guidance helped us in this regard. \par

\pagebreak
\end{document}